Design Principles from Glass Sponges \\for Structurally Robust Lattices

### 2018-12-09 Paper-FernandesWeaverBertoldi_AdvMaterials_2018.tex
.

\begin{figure*}[!htb]
	\centering
	\captionsetup{width=0.8\textwidth}
	\includegraphics[width=0.9\textwidth]{Fig2}
	\caption{\textbf{Experimental Results.} (a)-(d) shows the different designs (\emph{Design A-D}) considered in this analysis. (e) shows the experimental stress-strain curve as well as the overlaid numerical results for linear stiffness and critical buckling for the different designs considered.(f) shows the undeformed experimental setup for the different designs.}\label{Fig2}
\end{figure*}

@@

We began our analysis by testing samples of the four considered designs comprising a tessellation of $6\times6$ square cells with $L=1.91$ cm. The samples were fabricated with a multi-material 3D printer \mf{(add model @James)} using \KB{name of material} \mf{add info here @James} and compressed uniaxially  using  an Instron Model 5969 with 50kN capacity  (\Cref{Fig2}(e)). \KB{switch labels (f) and (e) in Fig 2} %Using this set-up, we tested three replicas of each design that were 3D printed and tested on different days.
The results reported in \Cref{Fig2}(f)  show that all structures are characterized by an initial linear behavior, a sudden departure from linearity caused by in-plane buckling and catastrophic failure following immediately thereafter.   Furthermore, it is also important to note that all  designs with diagonal reinforcement (i.e. \emph{Designs A-C}) overlay each other in the linear regime. Focusing on the initial linear regime, we find that  the different diagonal reinforcement designs considered do not impact the structure's overall stiffness (i.e. the initial stiffness of Designs A, B and C is identical). Design D, as expected, has a higher stiffness because of its thicker vertical and horizontal element's. However, it fails much earlier due to a shorter critical buckling strain. On the other hand, \emph{Design A} (the sponge design) outperforms the  considered structures in the amount of load it can bare before the onset of buckling occurs and provides the best mechanical performance without compromising the structural stiffness.

Next, we use Finite Element (FE) simulations conducted using the commercial software ABAQUS/Standard to further understand how the double diagonal system found in the \textit{Euplectella Aspergilum} results in significantly improved mechanical performance.  All our models are constructed using  Timoshenko beam elements (Abaqus element type \KB{B??}) and the material's response is captured using an isotropic linear elastic materials. We start by simulating the response of the  6 by 6 specimens tested in our experiments and find  very good agreement  between our experiments and numerical model (see Fig. \KB{??}).  Having validated our numerical analysis, we next use them to investigate \KB{what??? big picture of Fig 3} the To reduce the computational cost, we took advantage of the periodicity of the structures and investigated their response  by considering a Representative Volume Element (RVE) with periodic boundary conditions along the free edges of the unit cell (more information on this can be found in the SI). For our numerical model we assume Timoshenko beam elements with uniform circular cross-sections and pin-joints at beam intersections. In an effort to create a method for impartial comparison, we maintain a constant total mass (or constant volume as the material is assumed to be incompressible) between all of the designs, as well as a constant mass ratio between diagonal and non-diagonal elements for designs containing these diagonal reinforcement.

The results presented in \cref{Fig3}(a) show that all of the structures containing diagonal reinforcement behave the same way for varying loading angles. This illustrates the fact that the structural stiffness is independent of design, but instead depend on the amount of material allocated to the perpendicular aligned beam elements. This is further supported by the graph for \emph{Design D}, where all of the material from the diagonal beams is removed and allocated to the non-diagonal elements, giving the structure a higher stiffness at $0^\circ$ and lower stiffness at $45^\circ$. Any stiffness at $45^\circ$ in Design D is strictly a result of the bending resistance due to the pinned joints between the non-diagonal beams.

@@

%In order to study the impact of diagonal separation for Design A (sponge design), we perform a parametric study on the buckling behavior of the structure under varying separation distances ($C$). Note, we do not perform a stiffness test as the linear stiffness is not dependent on design but instead depends on the mass ratio between diagonal and non-diagonal elements as well as the diagonal element's angles. {Fig5}(a) shows the buckling behavior as a function of the non-dimensional separation ($C/L$). Where at $C/L=0$ we obtain Design B, and at $C/L=0.5$ we obtain diamond shaped reinforcement alignment.

%To investigate the effect of mass ratio on the properties of the structure, we parametrize the allocation of mass between the diagonal elements and the non-diagonal elements. To quantitatively describe this mass ratio, we introduce the variable $\lambda$ as the fraction $V_{nd}/V_d$, where $V_{nd}$ describes the collective volume of all non-diagonal elements and $V_d$ is the collective volume of all diagonal elements in the unit cell. It is important to note, that for all simulations varying $\lambda$ we maintain the same total mass of the structure, namely $V_{nd}+V_d=\mbox{const. } \forall (V_{nd},V_d)$.

>>>>

\begin{figure*}[!htb]
	\centering
	\captionsetup{width=0.8\textwidth}
	\includegraphics[width=0.9\textwidth]{Fig2}
	\caption{\textbf{Experimental Results.} (a)-(d) shows the different designs (\emph{Design A-D}) considered in this analysis. (e) shows the undeformed experimental setup for the different designs. (f) shows the experimental stress-strain curve as well as the overlaid numerical results for linear stiffness and critical buckling for the different designs considered.}\label{Fig2}
\end{figure*}

@@

We began our analysis by testing samples of the four considered designs comprising a tessellation of $6\times6$ square cells with $L=1.91$ cm. The samples were fabricated with a multi-material 3D printer \mf{(add model @James)} using \KB{name of material @James} and compressed uniaxially using an Instron Model 5969 with 50kN capacity (\Cref{Fig2}(e)). For each design, we 3D print three separate specimens that are then reported in \cref{Fig2}(f). The results reported in \Cref{Fig2}(f) show that all structures are characterized by an initial linear behavior, a sudden departure from linearity caused by in-plane buckling and catastrophic failure following immediately thereafter. Furthermore, it is also important to note that all designs with diagonal reinforcement (i.e. \emph{Designs A-C}) overlay each other in the linear regime. Focusing on the initial linear regime, we find that  the different diagonal reinforcement designs considered do not impact the structure's overall stiffness (i.e. the initial stiffness of Designs A, B and C are identical). Design D, as expected, has a higher stiffness because of its thicker vertical and horizontal elements. However, it fails much earlier due to a shorter critical buckling strain. On the other hand, \emph{Design A} (the sponge design) outperforms the considered structures in the amount of load it can bare before the onset of buckling occurs and provides the best mechanical performance without compromising the structural stiffness while using the same total amount of material.

Next, we use Finite Element (FE) simulations conducted with the widely used commercial software ABAQUS/Standard to further understand how the double diagonal system found in the \textit{Euplectella Aspergilum} results in significantly improved mechanical performance. All our models are constructed using Timoshenko beam elements (ABAQUS element type B22) and the material's response is captured using an isotropic linear elastic materials. We start by simulating the response of the 6 by 6 specimens tested in our experiments and find very good agreement between our experiments and numerical model (see \cref{Fig2}(f)). Having validated our numerical analysis with experimental results, we next use the numerical model to investigate the first-order behavior of the structure (neglecting all edge effects by the assumption of an infinite periodic structure). To reduce the computational cost, we took advantage of the periodicity of the structures and investigated their response by considering a Representative Volume Element (RVE) with periodic boundary conditions along the free edges of the unit cell (more information on this can be found in the SI). In an effort to create a method for impartial comparison, we maintain a constant total mass (or constant volume as the material is assumed to be incompressible) between all of the designs, as well as a constant mass ratio between diagonal and non-diagonal elements for the designs containing diagonal reinforcement.

The results presented in \cref{Fig3}(a) show that all of the structures containing diagonal reinforcement behave the same way for varying loading angles. This illustrates the fact that the structural stiffness is independent of design, but instead depend on the amount of material allocated to elements aligned parallel to the angle of loading. This is further supported by the graph for \emph{Design D}, where all of the material from the diagonal beams is removed and allocated to the non-diagonal elements, giving the structure a higher stiffness at $0^\circ$ and lower stiffness at $45^\circ$. Any stiffness at $45^\circ$ in Design D is strictly a result of the bending resistance due to the pinned joints between the non-diagonal beams.

@@

Multiplying the results of \cref{Fig3}(a) together with \cref{Fig3}(b) provides a measure of the normalized critical buckling load as seen in \cref{Fig3}(c). From these results, we clearly see that the geometric benefit attributed to \emph{Design A} clearly propagates through all loading angles. The benefit presented, is substantial near $0^\circ$ loading angles from all other designs. For loading angles near $\approx 45 ^\circ$, \emph{Design A} still outperforms \emph{Design B} and \emph{Design C}. However, it is important to note that \emph{Design D} appears to have a benefit over \emph{Design A} in this regime. This benefit, however, is attributed to numerical constraints imposed by the periodic boundary conditions. When creating a finite size structure and omit and peridic boundary conditions from our model, we see the benefit of \emph{Design D} over \emph{Design A} vanish and \emph{Design A} outperforms over all other considered designs for all loading angles. This further benefit for \emph{Design A} is attributed to it's insensitivity to edge effects. Furthermore, from \cref{Fig3}(e), we can see that \emph{Design A}, \emph{Design B}, \emph{Design C} have periodic buckling modes that are note dependent on the domain size, whereas for \emph{Design D}, the buckling mode strongly depends on the domain size (find further analysis on varying loading angles in the SI.)
